---
title: "R work with Rural Economy data"
output: html_notebook
---

## Getting packages.

```{r}
install.packages("pacman")
library(pacman)
p_load(pacman, ggplot2, tidyverse, rio, magrittr)
```

Reshaping the rural econ data set given in the general repository.

```{r}
#Importing the dataset
df <- import("rural-econ.csv") %>%
  as_tibble() %>%
  print()

#Reshaping the data to a wide dataframe
df %<>% spread(key = Attribute, value = Value)

#Checking features
df %>% print()
df %>% glimpse()

#Filter for when wanting to select specific areas or states
# df %<>% filter(State == "AR")

#Writing this new data to a file for later use
df %>% write.csv("rural-econ-edit.csv")
```

Reshaping the veterans data set from the same USDA study.

```{r}
#Importing the dataset
df <- import("Rural_Atlas_Update24/Veterans.csv") %>%
  as_tibble() %>%
  print()

#Filter for when wanting to select specific areas or states
# df %<>% filter(State == "AR")

#Checking features
df %>%
  print()

#Reshaping the data into a wide format
df %<>% spread(key = Attribute, value = Value)

#Writing the new dataframe into a file
df %>% write.csv("veterans-edit.csv")
```

Joining the new data together into one data frame and fixing column names.

```{r}
#Importing the rural econ reshaped data
df <- import("rural-econ-edit.csv") %>%
  as_tibble()

#Importing the veterans reshaped data
otherdf <- import("veterans-edit.csv") %>%
  as_tibble()

#Joining the data frames
newdf <- df %>% full_join(otherdf, by="FIPS") %>%
  print()

#Checking column names
newdf %>% colnames()

#Renaming columns that are strange
newdf %<>% rename("State" = State.x,
                  "County" = County.x,
                  "V1" = V1.x)

#Removing duplicate columns
newdf %<>% select(-c(V1.y:County.y))

#Checking the data frame again and column names
newdf %>% glimpse()

#Seeing if any values are missing
any(is.na(newdf))

#Writing this joined data frame to a file
newdf %>% write.csv("VetsAndPoverty.csv")

```


```{r}
df <- import("ARVetsAndPoverty.csv") %>%
  as_tibble()


df %>%
  ggplot(aes(x =Vets18OPct, 
             y = Poverty_Rate_ACS)) + 
  geom_point() +
  theme(legend.position = "bottom")

df %>%
  ggplot(aes(x = County,
             y = Poverty_Rate_ACS)) +
  geom_col() +
  theme(legend.position = "bottom")
```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
